\thetitle

### 2021-05-04 paper/paper.tex
paper

% a discount factor of \(0.99\).

% \definecolor{lightgray}{rgb}{0.83, 0.83, 0.83}
% \begin{table}[tb]
%   \begin{center}
%     \begin{tabular}{c|ccc|c|c||c}
%       \hline
%       70-\(\Exp\)-\(\Unif\) & WIPC & FGIC & BOC & FGIC+BOC & SUM & SFTT & SL(\%) \\
%       \hline                &
%        ESSLTA{}             &      &      &     &          &     &      &        \\
%        ANN{}                &      &      &     &          &     &      &        \\
%        ESSLTB{}             &      &      &     &          &     &      &        \\
%        BILD{}               &      &      &     &          &     &      &        \\
%       \hline                &
% %
%       \hline                &
%       70-\(\Unif\)-\(\Exp\) & WIPC & FGIC & BOC & FGIC+BOC & SUM & SFTT & SL(\%) \\
%       \hline                &
%        ESSLTA{}             &      &      &     &          &     &      &        \\
%        ANN{}                &      &      &     &          &     &      &        \\
%        ESSLTB{}             &      &      &     &          &     &      &        \\
%        BILD{}               &      &      &     &          &     &      &        \\
%       \hline                &
% %
%       \hline                &
%       70-\(\Exp\)-\(\Exp\)  & WIPC & FGIC & BOC & FGIC+BOC & SUM & SFTT & SL(\%) \\
%       \hline                &
%        ANN{}                &      &      &     &          &     &      &        \\
%        ESSLTA{}             &      &      &     &          &     &      &        \\
%        ESSLTB{}             &      &      &     &          &     &      &        \\
%        BILD{}               &      &      &     &          &     &      &        \\
%     \end{tabular}
%   \end{center}
%   \caption{\label{tbl:70} Results for a bottleneck utilisation of 70\%. }
% \end{table}

\MS[t]{Exp - Exp in simulation model?}
\begin{table}[tb]
  \begin{center}
    \begin{tabular}{c|rrr|c|c||c|c|c|c|c}
      \toprule
      80-\(\Exp\)-\(\Unif\)   & WIPC   & FGIC    & BOC      & FGIC+BOC & SUM     & SFTT  & SFTT+FGIT & SL(\%) & Cost.p.P & \(\avgrew^{\pol}\) \\
      \midrule
      \rl{0.995}              &  &  &  &          &  &  &    &   &    &              \\
      \rl{1.000}              &  &  &  &          &  &  &    &   &    &              \\
      \ql{1.000}              &  &  &  &          &  &  &    &   &    &              \\
      \BILOne{}               &  &  &  &          &  &  &    &   &    &              \\
      \BILTwo{}               &  &  &  &          &  &  &    &   &    &              \\
      \BILThree{}             &  &  &  &          &  &  &    &   &    &              \\
      \bottomrule
%
%       \hline
%       80-\(\Unif\)-\(\Exp\) & WIPC   & FGIC    & BOC      & FGIC+BOC & SUM     & SFTT  & SFTP+FGI & SL(\%) & Cost.p.P & \(\avgrew^{\pol}\) \\
%       \hline                &
%        ESSLTA{}             &        &         &          &          &         &       &          &        &          &                    \\
%        ANN{}                &        &         &          &          &         &       &          &        &          &                    \\
%        ESSLTB{}             &        &         &          &          &         &       &          &        &          &                    \\
%        BILD{}               &        &         &          &          &         &       &          &        &          &                    \\
%       \hline
% %
%       \hline
%       80-\(\Exp\)-\(\Exp\)  & WIPC   & FGIC    & BOC      & FGIC+BOC & SUM     & SFTT  & SFTP+FGI & SL(\%) & Cost.p.P & \(\avgrew^{\pol}\) \\
%       \hline                &
%        ANN{}                &        &         &          &          &         &       &          &        &          &                    \\
%        ESSLTA{}             &        &         &          &          &         &       &          &        &          &                    \\
%        ESSLTB{}             &        &         &          &          &         &       &          &        &          &                    \\
%        BILD{}               &        &         &          &          &         &       &          &        &          &                    \\
    \end{tabular}
  \end{center}
  \caption{\label{tbl:80} Results for a bottleneck utilisation of 80\%. }
\end{table}

% \definecolor{lightgray}{rgb}{0.83, 0.83, 0.83}
% \begin{table}[tb]
%   \begin{center}
%     \begin{tabular}{c|ccc|c|c||c}
%       \hline
%       80-\(\Exp\)-\(\Unif\)   & WIPC      & FGIC      & BOC       & FGIC+BOC  & SUM   & SL(\%) \\
%       \hline
%        ESSLTA{}     &           &           &           &           &       &                  \\
%        ANN{}        &           &           &           &       &       &                      \\
%        ESSLTB{}     &           &           &           &       &       &                      \\
%        BILD{}       &           &           &           &       &       &                      \\
%       \hline
% %
%       \hline
%       80-\(\Unif\)-\(\Exp\)   & WIPC      & FGIC      & BOC       & FGIC+BOC  & SUM    & SL(\%) \\
%       \hline
%        ESSLTA{}     &           &           &           &           &       &      \\
%        ANN{}        &           &           &           &           &       &      \\
%        ESSLTB{}     &           &           &           &           &       &      \\
%        BILD{}       &           &           &           &           &       &      \\
%       \hline
% %
%       \hline
%       80-\(\Exp\)-\(\Exp\) & WIPC     & FGIC      & BOC       & FGIC+BOC  & SUM   & SL(\%) \\
%       \hline
%        ANN{}     &          &           &           &           &       &      \\
%        ESSLTA{}  &          &           &           &           &       &      \\
%        ESSLTB{}  &          &           &           &           &       &      \\
%        BILD{}    &          &           &           &           &       &      \\
%     \end{tabular}
%   \end{center}
%   \caption{\label{tbl:80} Results for a bottleneck utilisation of 70\%. }
% \end{table}

@@

>>>>

  % a discount factor of \(0.99\).
  %    demandUnif65_145            -- 90%   -- 6.
  % -- demandUnif78_158 -- 80%   -- 3.
  % -- demandUnif95_175  -- 70%   -- 1.
  % -- demandExp105  -- 90%           -- 5.
  % -- demandExp118  -- 80%          -- 4.
  % -- demandExp135  -- 70%          -- 2.

\MS[t]{Exp - Exp in simulation model?}
 \begin{table}[tb]
  \begin{center}
    \begin{tabular}{crrrccccccc}
      % \toprule
      % 70-\(\Unif\) & WIPC              & FGIC              & BOC                & FGIC+BOC                        & SUM                & SFTT          & FGIT                & SL(\%)       & Cost.p.P             & \(\avgrew^{\pol}\) \\
      % \midrule
      % \ql{0.99}    & \cost{38776.300}  & \cost{133872.800} & \cost{82673.600 }  &                                 & \cost{255322.700}  & \timem{1.340} & \timem{2.558}       & \tard{0.095} &                      &                    \\
      % \rl{0.99}    & \cost{37111.000}  & \cost{113425.600} & \cost{98654.400 }  &                                 & \cost{249191.000}  & \timem{1.305} & \timem{2.412}       & \tard{0.110} &                      &                    \\
      % \rl{1.00}    & \cost{38755.000}  & \cost{156444.000} & \cost{59718.400 }  &                                 & \cost{254917.400}  & \timem{1.339} & \timem{2.679}       & \tard{0.068} &                      &                    \\
      % \BILOne{}    & \cost{32159.900}  & \cost{     0.000} & \cost{514558.400}  &                                 & \cost{546718.300}  & \timem{1.202} & \timem{1.693}       & \tard{0.552} &                      &                    \\
      % \BILTwo{}    & \cost{32169.900}  & \cost{ 83391.200} & \cost{106219.200}  &                                 & \cost{221780.300}  & \timem{1.202} & \timem{2.143}       & \tard{0.114} &                      &                    \\
      % \BILThree{}  & \cost{32239.800}  & \cost{247416.800} & \cost{21382.400 }  &                                 & \cost{301039.000}  & \timem{1.204} & \timem{3.029}       & \tard{0.022} &                      &                    \\
      % \BILFour{}   & \cost{32262.600}  & \cost{428865.200} & \cost{5483.200  }  &                                 & \cost{466611.000}  & \timem{1.204} & \timem{4.007}       & \tard{0.006} &                      &                    \\
      % \bottomrule
      \toprule
      70-\(\Unif\)   & WIPC              & FGIC              & BOC                & FGIC+BOC                        & SUM                & SFTT          & FGIT                & SL(\%)       & Cost.p.P             & \(\avgrew^{\pol}\) \\
      \midrule
      \ql{0.99}      & \cost{38563.000}  & \cost{134703.600} & \cost{81704.800}   & \fgiboc{134703.600}{81704.800}  & \cost{254971.400}  & \timem{1.335} & \fgit{1.335}{2.558} & \tard{0.094} & \costpp{254971.400}  &                    \\
      \rl{0.99}      & \cost{37197.750}  & \cost{113100.800} & \cost{100398.400}  & \fgiboc{113100.800}{100398.400} & \cost{250696.950}  & \timem{1.307} & \fgit{1.307}{2.412} & \tard{0.111} & \costpp{250696.950}  & \rnd{35.040}       \\
      \rl{1.00}      & \cost{38659.100}  & \cost{156659.200} & \cost{59743.200}   & \fgiboc{156659.200}{59743.200}  & \cost{255061.500}  & \timem{1.338} & \fgit{1.338}{2.678} & \tard{0.068} & \costpp{255061.500}  & \rnd{36.501}       \\
      \BILOne{}      & \cost{32056.500}  & \cost{0.000}      & \cost{512904.000}  & \fgiboc{0.000}{512904.000}      & \cost{544960.500}  & \timem{1.200} & \fgit{1.200}{1.691} & \tard{0.551} & \costpp{544960.500}  &                    \\
      \BILTwo{}      & \cost{32063.850}  & \cost{83461.000}  & \cost{105009.600}  & \fgiboc{83461.000}{105009.600}  & \textbf{\cost{220534.450}}  & \timem{1.200} & \fgit{1.200}{2.142} & \tard{0.114} & \textbf{\costpp{220534.450}}  &                    \\
      \BILThree{}    & \cost{32155.150}  & \cost{247727.000} & \cost{21680.800 }  & \fgiboc{247727.000}{21680.800 } & \cost{301562.950}  & \timem{1.202} & \fgit{1.202}{3.029} & \tard{0.022} & \costpp{301562.950}  &                    \\
      \BILFour{}     & \cost{32140.550}  & \cost{429097.800} & \cost{5076.800 }   & \fgiboc{429097.800}{5076.800 }  & \cost{466315.150}  & \timem{1.202} & \fgit{1.202}{4.007} & \tard{0.005} & \costpp{466315.150}  &                    \\
      \bottomrule
      \toprule
      80-\(\Unif\)   & WIPC              & FGIC              & BOC                & FGIC+BOC                        & SUM                & SFTT          & FGIT                & SL(\%)       & CostpP               & \(\avgrew^{\pol}\) \\
      \midrule
      \ql{0.99}      & \cost{63095.100}  & \cost{180403.800} & \cost{121528.000}  & \fgiboc{180403.800}{121528.000} & \textbf{\cost{365026.900}}  & \timem{1.680} & \fgit{1.680}{3.019} & \tard{0.103} & \textbf{\costpp{365026.900}} &                    \\
      \rl{0.99}      & \cost{65310.650}  & \cost{168489.200} & \cost{148593.600}  & \fgiboc{168489.200}{148593.600} & \cost{382393.450}  & \timem{1.721} & \fgit{1.721}{3.005} & \tard{0.136} & \costpp{382393.450}  & \rnd{52.918}       \\
      \rl{1.00}      & \cost{60778.500}  & \cost{234045.000} & \cost{76168.000}   & \fgiboc{234045.000}{76168.000}  & \cost{370991.500}  & \timem{1.637} & \fgit{1.637}{3.226} & \tard{0.066} & \costpp{370991.500}  & \rnd{52.291}       \\
      \BILOne{}      & \cost{51888.650}  & \cost{0.000}      & \cost{830218.400}  & \fgiboc{0.000}{830218.400}      & \cost{882107.050}  & \timem{1.474} & \fgit{1.474}{1.968} & \tard{0.672} & \costpp{882107.050}  &                    \\
      \BILTwo{}      & \cost{51998.950}  & \cost{70108.800}  & \cost{255166.400}  & \fgiboc{70108.800}{255166.400}  & \cost{377274.150}  & \timem{1.476} & \fgit{1.476}{2.298} & \tard{0.206} & \costpp{377274.150}  &                    \\
      \BILThree{}    & \cost{51976.550}  & \cost{240175.000} & \cost{77822.400}   & \fgiboc{240175.000}{77822.400}  & \cost{369973.950}  & \timem{1.475} & \fgit{1.475}{3.091} & \tard{0.060} & \costpp{369973.950}  &                    \\
      \BILFour{}     & \cost{51827.050}  & \cost{442307.600} & \cost{26711.200}   & \fgiboc{442307.600}{26711.200}  & \cost{520845.850}  & \timem{1.472} & \fgit{1.472}{4.031} & \tard{0.019} & \costpp{520845.850}  &                    \\
      \bottomrule
      \toprule
      90-\(\Unif\)   & WIPC              & FGIC              & BOC                & FGIC+BOC                        & SUM                & SFTT          & FGIT                & SL(\%)       & CostpP               & \(\avgrew^{\pol}\) \\
      \midrule
      \ql{0.99}      & \cost{98909.150}  & \cost{190681.000} & \cost{297333.600}  & \fgiboc{190681.000}{297333.600} & \cost{586923.750}  & \timem{2.133} & \fgit{2.133}{3.417} & \tard{0.173} & \costpp{586923.750}  &                    \\
      \rl{0.99}      & \cost{105348.200} & \cost{263950.600} & \cost{207183.200}  & \fgiboc{263950.600}{207183.200} & \textbf{\cost{576482.000}}  & \timem{2.238} & \fgit{2.238}{3.825} & \tard{0.121} & \textbf{\costpp{576482.000}}  & \rnd{79.826}       \\
      \rl{1.00}      & \cost{107873.800} & \cost{240798.800} & \cost{253865.600}  & \fgiboc{240798.800}{253865.600} & \cost{602538.200}  & \timem{2.280} & \fgit{2.280}{3.771} & \tard{0.153} & \costpp{602538.200}  & \rnd{80.425}       \\
      \BILOne{}      & \cost{88658.100}  & \cost{0.000}      & \cost{1418529.600} & \fgiboc{0.000}{1418529.600}     & \cost{1507187.700} & \timem{1.964} & \fgit{1.964}{2.462} & \tard{0.790} & \costpp{1507187.700} &                    \\
      \BILTwo{}      & \cost{88317.700}  & \cost{50854.400}  & \cost{646000.800}  & \fgiboc{50854.400}{646000.800}  & \cost{785172.900}  & \timem{1.958} & \fgit{1.958}{2.666} & \tard{0.355} & \costpp{785172.900}  &                    \\
      \BILThree{}    & \cost{88252.450}  & \cost{207210.600} & \cost{299885.600}  & \fgiboc{207210.600}{299885.600} & \cost{595348.650}  & \timem{1.957} & \fgit{1.957}{3.309} & \tard{0.148} & \costpp{595348.650}  &                    \\
      \BILFour{}     & \cost{87774.600}  & \cost{415178.200} & \cost{153612.800}  & \fgiboc{415178.200}{153612.800} & \cost{656565.600}  & \timem{1.950} & \fgit{1.950}{4.158} & \tard{0.071} & \costpp{656565.600}  &                    \\
      \bottomrule
    \end{tabular}
  \end{center}
  \caption{\label{tbl:unif} Results with moderate variability in the system due to uniformly
    distributed demand interarrival times. }
\end{table}

\begin{comment}
* Unif-70%

           QL	AvgQL0.99	AvgQL1.0	BIL1	    BIL2	  BIL3	  BIL4
P_1    251303	   243743	  259512	540549	213541	295577	467766
P_2    264665	   247607	  253436	533630	217064	296323	466820
P_3    260043	   257121	  256038	564332	232896	303723	465187
P_4    250869	   256036	  254776	541620	221602	301724	465467
P_5    254079	   250814	  252465	546975	225815	300616	468210
P_6    247780	   248298	  254246	549508	220674	300177	467039
P_7    265459	   248659	  257828	546295	220635	305236	464263
P_8    251896	   245786	  254077	544850	219209	301524	466451
P_9    254502	   245544	  254622	545734	221235	302580	466944
P_10   252631	   248302	  252174	553690	225132	302910	467963
P_11   253068	   258304	  253873	539393	216099	302757	465670
P_12   260997	   254848	  250599	547757	227971	303835	463119
P_13   253329	   248691	  256341	549066	219881	306322	469024
P_14   254715	   267491	  259271	559487	216614	304241	465459
P_15   251007	   248119	  259367	528088	213454	301483	464478
P_16   254686	   250503	  257132	552262	219856	304220	466426
P_17   250830	   249925	  255187	529669	214652	298888	468042
P_18   259411	   249452	  252322	545394	217661	298885	464701
P_19   261476	   240635	  256826	535296	224470	300230	465799
P_20   246682	   254061	  251138	545615	222228	300008	467475

- Friedman chi-squared statistic: 112.778571
- p-value: 5.335902e-22
- This p-value is for rejection of the omnibus null hypothesis, that all samples (groups) are from
  the same distribution, i.e. there is no effect of groups. The alternate hypothesis that one or
  more of the correlated samples (groups) is different, i.e. there is a group effect.
- The omnibus p-value is at or below the respectable critical threshold of 0.05, so post-hoc
  pairwise multiple comparison tests are conducted to discern which of the pairs have significantly
  differences. Post-hoc tests conducted: Conover, where the p-value is adjusted by the false
  discovery rate (FDR) procedure of Benjaminyi-Hochberg.

  Post-hoc p-values of all possible pairs (of samples/ groups) are compactly represented as a lower
  triangular matrix. Each numerical entry is the p-value of row/column pair, i.e. the null
  hypotheses that the group represented by a particular column name is different from the group
  represented by a particular row name. Conover p-values, further adjusted by the
  Benjaminyi-Hochberg FDR method

  * Unif-80%

      QL	AvgQL0.99	AvgQL1.0	BIL1	    BIL2	  BIL3	  BIL4
      \ql{0.99} \rl{0.99} \rl{1.00} \BILOne{} \BILTwo{} \BILThree{} \BILFour{}
P_1  387809	388915	383835	885904	393992	398202	514142
P_2  359157	379690	363164	886975	384114	376660	515336
P_3  383065	376724	360581	894013	379834	360186	520716
P_4  376629	379476	381806	882742	360301	358114	528800
P_5  347754	383895	370965	864484	375807	366606	523167
P_6  357321	384470	369683	871624	366181	364609	530412
P_7  358944	383526	358428	911472	366868	363209	514686
P_8  347414	376654	385126	895509	392616	383019	532197
P_9  360972	383002	369881	899334	378537	355148	513209
P_10 357457	374808	368923	866065	355299	359736	513984
P_11 366141	373215	369628	860455	396973	377169	520757
P_12 368787	388541	361227	894268	378112	376437	513099
P_13 370668	397366	371919	900575	368307	357662	514924
P_14 388434	384845	375453	861305	399392	369540	522818
P_15 367029	381957	369656	884187	390026	362042	520379
P_16 367760	383548	371404	860149	363596	370414	530716
P_17 349081	372732	369545	855763	344912	353143	515141
P_18 361824	382886	372029	904230	376210	400139	531858
P_19 366121	398561	379479	889253	403883	378528	515531
P_20 358171	373058	367098	873834	370523	368916	525045

- Friedman chi-squared statistic: 90.578571
- p-value: 2.297453e-17
- rejection of the omnibus null hypothesis

* Unif-90%

      \ql{0.99} \rl{0.99} \rl{1.00} \BILOne{} \BILTwo{} \BILThree{} \BILFour{}
P_1   653676	521714	583292	1411442	701676	548748	673075
P_2   678801	606952	610287	1599513	862870	608274	655640
P_3   600219	602535	594998	1496442	864121	605376	630665
P_4   662569	518558	612290	1417290	835203	580285	657643
P_5   557821	607801	610968	1522469	859054	570829	680786
P_6   561714	553561	569823	1493178	776052	612004	621577
P_7   577479	538003	539180	1473951	790533	564949	704889
P_8   538715	603415	575945	1598306	798817	602557	610314
P_9   569077	528191	571533	1479493	713889	602314	631613
P_10   615113	527510	650835	1522554	744289	551199	598620
P_11   558858	561689	580324	1526107	755665	596688	643571
P_12   564356	564868	594560	1517267	730110	587742	616851
P_13   567569	619918	619763	1433219	755946	647755	730470
P_14   576338	619782	636887	1512337	800148	543174	681310
P_15   585967	581851	658242	1548853	907391	615699	652752
P_16   594172	609886	596591	1561824	836903	616500	718513
P_17   535899	570047	600196	1531139	707526	537206	621174
P_18   560293	612670	645596	1488537	782649	584652	673597
P_19   633629	571462	627070	1523982	745810	659741	683916
P_20   546210	609227	572384	1485851	734806	671281	644336

- Friedman chi-squared statistic: 96.150000
- p-value: 1.592809e-18
- rejection of the omnibus null hypothesis

\end{comment}

\begin{table}[tb]
  \begin{center}
    \begin{tabular}{crrrccccccc}
      \toprule
      70-\(\Exp\) & WIPC    & FGIC    & BOC     & FGIC+BOC & SUM     & SFTT     & FGIT & SL(\%)  & Cost.p.P & \(\avgrew^{\pol}\) \\
      \midrule
      \ql{0.99}   & \cost{53873.500} & \cost{142398.800} & \cost{164427.200} & \fgiboc{142398.800}{164427.200}  & \cost{360699.500} & \timem{1.585} & \fgit{1.585}{2.796}  & \tard{0.162} & \costpp{360699.500} & \\
      \rl{0.99}   & \cost{61419.850} & \cost{181702.200} & \cost{115287.200} & \fgiboc{181702.200}{115287.200}  & \cost{358409.250} & \timem{1.734} & \fgit{1.734}{3.145}  & \tard{0.107} & \costpp{358409.250} & \rnd{50.787} \\
      \rl{1.00}   & \cost{56578.800} & \cost{199310.000} & \cost{115714.400} & \fgiboc{199310.000}{115714.400}  & \cost{371603.200} & \timem{1.639} & \fgit{1.639}{3.136}  & \tard{0.113} & \costpp{371603.200} & \rnd{50.575} \\
      \BILOne{}   & \cost{48547.100} & \cost{     0.000} & \cost{776753.600} & \fgiboc{     0.000}{776753.600}  & \cost{825300.700} & \timem{1.479} & \fgit{1.479}{1.975}  & \tard{0.663} & \costpp{825300.700} & \\
      \BILTwo{}   & \cost{48618.850} & \cost{ 66927.200} & \cost{248638.400} & \fgiboc{ 66927.200}{248638.400}  & \cost{364184.450} & \timem{1.480} & \fgit{1.480}{2.312}  & \tard{0.220} & \costpp{364184.450} & \\
      \BILThree{} & \cost{48632.050} & \cost{222603.200} & \cost{ 74568.800} & \fgiboc{222603.200}{ 74568.800}  & \textbf{\cost{345804.050}} & \timem{1.481} & \fgit{1.481}{3.094}  & \tard{0.063} & \textbf{\costpp{345804.050}} & \\
      \BILFour{}  & \cost{48514.200} & \cost{409531.200} & \cost{ 23406.400} & \fgiboc{409531.200}{ 23406.400}  & \cost{481451.800} & \timem{1.478} & \fgit{1.478}{4.029}  & \tard{0.019} & \costpp{481451.800} & \\
      \bottomrule
      \toprule
      80-\(\Exp\) & WIPC    & FGIC    & BOC     & FGIC+BOC & SUM     & SFTT     & FGIT & SL(\%)  & Cost.p.P & \(\avgrew^{\pol}\) \\
      \midrule
      \ql{0.99}   & \cost{87706.700} & \cost{227485.400} & \cost{225150.400} & \fgiboc{227485.400}{225150.400}  & \cost{540342.500} & \timem{2.043} & \fgit{2.043}{3.541}  & \tard{0.166} & \costpp{540342.500} & \\
      \rl{0.99}   & \cost{89838.950} & \cost{253476.000} & \cost{185687.200} & \fgiboc{253476.000}{185687.200}  & \cost{529002.150} & \timem{2.078} & \fgit{2.078}{3.689}  & \tard{0.124} & \costpp{529002.150} & \rnd{70.527} \\
      \rl{1.00}   & \cost{87171.500} & \cost{242915.600} & \cost{198456.000} & \fgiboc{242915.600}{198456.000}  & \cost{528543.100} & \timem{2.034} & \fgit{2.034}{3.599} & \tard{0.134} & \costpp{528543.100} & \rnd{72.944} \\
      \BILOne{}   & \cost{78731.850} & \cost{     0.000} & \cost{1259709.60} & \fgiboc{     0.000}{1259709.60}  & \cost{1338441.45} & \timem{1.884} & \fgit{1.884}{2.382}  & \tard{0.771} & \costpp{1338441.450} & \\
      \BILTwo{}   & \cost{78203.150} & \cost{ 52303.200} & \cost{548736.000} & \fgiboc{ 52303.200}{548736.000}  & \cost{679242.350} & \timem{1.875} & \fgit{1.875}{2.602}  & \tard{0.350} & \costpp{679242.350} & \\
      \BILThree{} & \cost{79029.850} & \cost{200273.200} & \cost{242100.800} & \fgiboc{200273.200}{242100.800}  & \textbf{\cost{521403.850}} & \timem{1.890} & \fgit{1.890}{3.265}  & \tard{0.142} & \textbf{\costpp{521403.850}} & \\
      \BILFour{}  & \cost{79384.750} & \cost{395493.000} & \cost{116943.200} & \fgiboc{395493.000}{116943.200}  & \cost{591820.950} & \timem{1.896} & \fgit{1.896}{4.128}  & \tard{0.062} & \costpp{591820.950} & \\
      \bottomrule
      \toprule
      90-\(\Exp\) & WIPC    & FGIC    & BOC     & FGIC+BOC & SUM     & SFTT     & FGIT & SL(\%)  & Cost.p.P & \(\avgrew^{\pol}\) \\
      \midrule
      \ql{0.99}   & \cost{168655.950} & \cost{222145.800} & \cost{788662.400} & \fgiboc{222145.800}{788662.400}  & \cost{1179464.150} & \timem{3.134} & \fgit{3.134}{4.501}  & \tard{0.285} & \costpp{1179464.150} & \\
      \rl{0.99}   & \cost{158034.800} & \cost{212726.200} & \cost{701300.800} & \fgiboc{212726.200}{701300.800}  & \cost{1072061.800} & \timem{2.970} & \fgit{2.970}{4.300}  & \tard{0.281} & \costpp{1072061.800} & \rnd{115.801} \\
      \rl{1.00}   & \cost{160453.950} & \cost{286065.800} & \cost{539803.200} & \fgiboc{286065.800}{539803.200}  & \textbf{\cost{986322.950}} & \timem{3.007} & \fgit{3.007}{4.623}  & \tard{0.204} & \textbf{\costpp{986322.950}} & \rnd{109.907} \\
      \BILOne{}   & \cost{146835.900} & \cost{     0.000} & \cost{2349374.40} & \fgiboc{     0.000}{2349374.40}  & \cost{2496210.300} & \timem{2.796} & \fgit{2.796}{3.295}  & \tard{0.867} & \costpp{2496210.300} & \\
      \BILTwo{}   & \cost{143756.000} & \cost{ 34112.800} & \cost{1412752.00} & \fgiboc{ 34112.800}{1412752.00}  & \cost{1590620.800} & \timem{2.748} & \fgit{2.748}{3.380}  & \tard{0.529} & \costpp{1590620.800} & \\
      \BILThree{} & \cost{144278.250} & \cost{154146.800} & \cost{877450.400} & \fgiboc{154146.800}{877450.400}  & \cost{1175875.450} & \timem{2.756} & \fgit{2.756}{3.857}  & \tard{0.294} & \costpp{1175875.450} & \\
      \BILFour{}  & \cost{147077.800} & \cost{335070.400} & \cost{622141.600} & \fgiboc{335070.400}{622141.600}  & \cost{1104289.800} & \timem{2.800} & \fgit{2.800}{4.608}  & \tard{0.175} & \costpp{1104289.800} & \\
      \bottomrule
    \end{tabular}
  \end{center}
  \caption{\label{tbl:exp} Results with high variability in the system due to exponentially
    distributed interarrival times of the demand. }
\end{table}

\begin{comment}

* 70-Exp

      \ql{0.99} \rl{0.99} \rl{1.00} \BILOne{} \BILTwo{} \BILThree{} \BILFour{}
P_1   351947	374561	379567	834003	386432	362168	492681
P_2   347668	352692	378234	822817	364552	333854	479469
P_3   367401	390552	366704	864960	381170	361897	482144
P_4   368674	359179	387919	835193	381497	349521	479063
P_5   348052	359409	367586	818363	368443	346388	481219
P_6   372165	357376	385714	820607	381450	351540	477010
P_7   358072	353692	375693	799663	354775	342411	478984
P_8   359080	367498	371778	863328	387183	361328	484675
P_9   362323	351285	364367	839001	371559	335595	489409
P_10   363594	363521	361902	819961	367956	355976	482128
P_11   351111	351607	359002	806276	345417	336380	478077
P_12   360053	358579	372742	823191	343266	337228	481849
P_13   362083	355953	375080	800258	347386	334618	484658
P_14   362155	380252	375057	843183	354535	358173	479977
P_15   362034	352998	365647	817717	351729	338243	477084
P_16   368261	356893	379373	839426	367362	359818	471416
P_17   368115	346666	367777	806327	357377	342397	483288
P_18   356904	343756	367760	816272	361651	341250	489722
P_19   370278	342598	365683	818686	357727	328406	477375
P_20   354020	349118	364479	816782	352222	338890	478808

- Friedman chi-squared statistic: 100.242857
- p-value: 2.232967e-19
- rejection of the omnibus null hypothesis

* 80-Exp

      \ql{0.99} \rl{0.99} \rl{1.00} \BILOne{} \BILTwo{} \BILThree{} \BILFour{}
P_1  524150	491399	492299	1253359	627883	492535	576044
P_2  551981	537349	534693	1378972	702719	546737	629820
P_3  568969	541461	548726	1323977	685412	522401	579507
P_4  547969	596543	592121	1364182	705144	536206	590773
P_5  595489	518330	531775	1334075	658382	532177	639777
P_6  535908	566964	536670	1429615	731598	520384	572011
P_7  557047	518934	569058	1336778	648986	497168	563390
P_8  538454	540953	512740	1395377	724787	530955	586574
P_9  522057	547783	539467	1387591	709643	522574	604104
P_10  545500	524853	523222	1307334	710386	511576	591671
P_11  550026	519641	518909	1312791	661352	529574	602428
P_12  520436	513871	520666	1302676	627306	495800	579365
P_13  534303	530579	517976	1377731	693986	553154	570858
P_14  527004	530556	538978	1407617	740972	528730	663494
P_15  546023	548754	539483	1324827	759339	560228	594110
P_16  551856	525486	542790	1326459	673565	553607	582936
P_17  509943	494150	491463	1302608	648931	482086	581970
P_18  538290	482416	487062	1275391	608823	502715	558249
P_19  515500	518251	507451	1331100	627861	495598	567573
P_20  525945	531770	525313	1296369	637772	513872	601765

- Friedman chi-squared statistic: 97.628571
- p-value: 7.835701e-19
- rejection of the omnibus null hypothesis

      \ql{0.99} \rl{0.99} \rl{1.00} \BILOne{} \BILTwo{} \BILThree{} \BILFour{}
P_1   1252433	1173395	1024728	2399890	1655026	1159432	1012319
P_2   1074569	870660	941377	2341852	1466107	1214910	971734
P_3   1188157	965337	871242	2510900	1409012	1050054	1260441
P_4   911949	1044494	758677	2345507	1566310	1118957	1130965
P_5   1033474	897575	836501	2197182	1219749	998558	946565
P_6   1216651	1228266	933766	2692086	1685058	1391199	1272896
P_7   1015338	983438	1040244	2399295	1429570	958909	951637
P_8   1512067	878268	1430194	2565419	1444940	1067515	906021
P_9   1108092	1232311	1309534	2641681	1850877	1153341	1079572
P_10   1344449	1264977	968913	2375393	1761920	1118482	1042407
P_11   1188536	1274797	1168751	3040365	1669772	1673853	1853585
P_12   1271137	985585	915254	2327385	1599041	1175113	1205382
P_13   1337521	1080134	1114726	2410549	1531861	1078113	1003334
P_14   1347283	1098738	861594	2728058	1566173	1387567	916554
P_15   1060109	1000957	947592	2422075	1704239	1016923	1070665
P_16   1095527	922726	957775	2363731	1637310	1232300	1017197
P_17   1157196	1095892	1011316	2669102	1959411	1245607	1212991
P_18   1171769	1047445	804936	2506905	1765175	1140291	1122519
P_19   1162809	1312587	949697	2481932	1361007	1166369	1052711
P_20   1140217	1083654	879642	2504899	1529858	1170016	1056301

- Friedman chi-squared statistic: 85.800000
- p-value: 2.253674e-16
- rejection of the omnibus null hypothesis

\end{comment}

@@

\section{}

\begin{table}
  \begin{center}
    \begin{tabular}{lP{1.75cm}P{1.75cm}P{1.75cm}P{1.75cm}P{1.75cm}P{1.75cm}}
      \toprule
      70-\(\Unif\) & \ql{0.99} & \rl{0.99} & \rl{1.00} & \BILOne{} & \BILTwo{} & \BILThree{} \\
      \midrule
      \rl{0.99}    & 3.37e-04  &           &           &           &           &             \\
      \rl{1.0}     & 3.55e-01  & 1.04e-05  &           &           &           &             \\
      \BILOne{}    & 1.94e-45  & 2.48e-51  & 6.90e-44  &           &           &             \\
      \BILTwo{}    & 1.09e-24  & 3.35e-16  & 9.57e-27  & 3.66e-64  &           &             \\
      \BILThree{}  & 1.78e-20  & 9.27e-29  & 2.44e-18  & 1.35e-22  & 6.26e-47  &             \\
      \BILFour{}   & 6.30e-34  & 3.85e-41  & 4.83e-32  & 1.16e-08  & 3.00e-56  & 1.16e-08    \\
      \bottomrule
      \toprule
      80-\(\Unif\) & \ql{0.99} & \rl{0.99} & \rl{1.00} & \BILOne{} & \BILTwo{} & \BILThree{} \\
      \midrule
      \rl{0.99}    & 4.78e-16  &           &           &           &           &             \\
      \rl{1.00}    & 5.26e-04  & 3.96e-08  &           &           &           &             \\
      \BILOne{}    & 1.02e-40  & 1.98e-21  & 3.92e-34  &           &           &             \\
      \BILTwo{}    & 6.98e-10  & 7.12e-03  & 2.06e-03  & 1.31e-27  &           &             \\
      \BILThree{}  & 2.16e-02  & 8.93e-11  & 2.03e-01  & 1.57e-36  & 2.46e-05  &             \\
      \BILFour{}   & 6.16e-33  & 1.10e-11  & 2.74e-25  & 5.33e-05  & 5.38e-18  & 5.30e-28    \\
      \bottomrule
      \toprule
      90-\(\Unif\) & \ql{0.99} & \rl{0.99} & \rl{1.00} & \BILOne{} & \BILTwo{} & \BILThree{} \\
      \midrule
      \rl{0.99}    & 5.18e-01  &           &           &           &           &             \\
      \rl{1.00}    & 1.94e-04  & 1.56e-05  &           &           &           &             \\
      \BILOne{}    & 8.40e-42  & 9.61e-43  & 1.10e-34  &           &           &             \\
      \BILTwo{}    & 2.36e-33  & 1.10e-34  & 5.21e-25  & 1.56e-05  &           &             \\
      \BILThree{}  & 4.16e-04  & 3.64e-05  & 8.19e-01  & 6.27e-35  & 1.81e-25  &             \\
      \BILFour{}   & 2.33e-20  & 6.57e-22  & 1.79e-11  & 2.93e-18  & 4.39e-08  & 5.97e-12    \\
      \bottomrule
    \end{tabular}
  \end{center}
  \caption{\label{tbl:stats-unif}Results from the statistical analysis for the results of of
    moderate variability in the system. }
\end{table}
